---
title: "Stock Analysis"
author: "Saurav"
date: "8/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Create the data files
```{r BAC,echo=FALSE, message=FALSE, warning=FALSE}
GS <- read.csv("~/Documents/515/515-Project/data/GS.csv")
JPM <- read.csv("~/Documents/515/515-Project/data/JPM.csv")
DTE <- read.csv("~/Documents/515/515-Project/data/DTE.csv")
AES <- read.csv("~/Documents/515/515-Project/data/AES.csv")
AAPL <- read.csv("~/Documents/515/515-Project/data/AAPL.csv")
AMZN <- read.csv("~/Documents/515/515-Project/data/AMZN.csv")

library(xts)
library(quantmod)
library(Rglpk)


date <- as.Date(GS$Date , format = "%Y-%m-%d")
GS <- cbind(date, GS[,-1])
GS <- GS[order(GS$date),]
data.GS <- xts(GS[,2:7],order.by=GS[,1])

names(data.GS) <-
paste(c("GS.Open","GS.High","GS.Low","GS.Close","GS.Adjusted","GS.Volume"))

GS[c(1:3,nrow(GS)),]


date <- as.Date(JPM$Date , format = "%Y-%m-%d")
JPM <- cbind(date, JPM[,-1])
JPM <- JPM[order(JPM$date),]
data.JPM <- xts(JPM[,2:7],order.by=JPM[,1])


names(data.JPM) <-
paste(c("JPM.Open","JPM.High","JPM.Low","JPM.Close","JPM.Adjusted","JPM.Volume"))

data.JPM[c(1:3,nrow(data.JPM)),]

date <- as.Date(AES$Date , format = "%Y-%m-%d")
AES <- cbind(date, AES[,-1])
AES <- AES[order(AES$date),]
data.AES <- xts(AES[,2:7],order.by=AES[,1])


names(data.AES) <-
paste(c("AES.Open","AES.High","AES.Low","AES.Close","AES.Adjusted","AES.Volume"))

data.AES[c(1:3,nrow(data.AES)),]


date <- as.Date(DTE$Date , format = "%Y-%m-%d")
DTE <- cbind(date, DTE[,-1])
DTE <- DTE[order(DTE$date),]
data.DTE <- xts(DTE[,2:7],order.by=DTE[,1])


names(data.DTE) <-
paste(c("DTE.Open","DTE.High","DTE.Low","DTE.Close","DTE.Adjusted","DTE.Volume"))

data.DTE[c(1:3,nrow(data.DTE)),]


date <- as.Date(AAPL$Date , format = "%Y-%m-%d")
AAPL <- cbind(date, AAPL[,-1])
AAPL <- AAPL[order(AAPL$date),]
data.AAPL <- xts(AAPL[,2:7],order.by=AAPL[,1])


names(data.AAPL) <-
paste(c("AAPL.Open","AAPL.High","AAPL.Low","AAPL.Close","AAPL.Adjusted","AAPL.Volume"))

data.AAPL[c(1:3,nrow(data.AAPL)),]

date <- as.Date(AMZN$Date , format = "%Y-%m-%d")
AMZN <- cbind(date, AMZN[,-1])
AMZN <- AMZN[order(AMZN$date),]
data.AMZN <- xts(AMZN[,2:7],order.by=AMZN[,1])


names(data.AMZN) <-
paste(c("AMZN.Open","AMZN.High","AMZN.Low","AMZN.Close","AMZN.Adjusted","AMZN.Volume"))

data.AMZN[c(1:3,nrow(data.AMZN)),]


data.JPM.Pandemic <- subset(data.JPM, index(data.JPM) >= "2019-07-01" &index(data.JPM) < "2021-08-01")
data.GS.Pandemic <- subset(data.GS, index(data.GS) >= "2019-07-01" &index(data.GS) < "2021-08-01")
data.AES.Pandemic <- subset(data.AES, index(data.AES) >= "2019-07-01" &index(data.AES) < "2021-08-01")
data.DTE.Pandemic <- subset(data.DTE, index(data.DTE) >= "2019-07-01" &index(data.DTE) < "2021-08-01")
data.AAPL.Pandemic <- subset(data.AAPL, index(data.AAPL) >= "2019-07-01" &index(data.AAPL) < "2021-08-01")
data.AMZN.Pandemic <- subset(data.AMZN, index(data.AMZN) >= "2019-07-01" &index(data.AMZN) < "2021-08-01")

JPM.Pandemic <- subset(JPM, JPM$date >= "2019-07-01" & JPM$date < "2021-08-01")
GS.Pandemic <- subset(GS, GS$date >= "2019-07-01" & GS$date < "2021-08-01")
AES.Pandemic <- subset(AES, AES$date >= "2019-07-01" & AES$date < "2021-08-01")
DTE.Pandemic <- subset(DTE, DTE$date >= "2019-07-01" & DTE$date < "2021-08-01")
AAPL.Pandemic <- subset(AAPL, AAPL$date >= "2019-07-01" & AAPL$date < "2021-08-01")
AMZN.Pandemic <- subset(AMZN, AMZN$date >= "2019-07-01" & AMZN$date < "2021-08-01")
```
Plotting the data for each security to check for missing data
```{r sec2 , echo=FALSE, message=FALSE, warning=FALSE}
summary(data.JPM)
plot(data.JPM$JPM.Close)

summary(data.GS)
plot(data.GS$GS.Close)

summary(data.AES)
plot(data.AES$AES.Close)

summary(data.DTE)
plot(data.DTE$DTE.Close)

summary(data.AAPL)
plot(data.AAPL$AAPL.Close)

summary(data.AMZN)
plot(data.AMZN$AMZN.Close)

```



Plot candlestick charts for each stocks using weeklty data

```{r candlestick , echo=FALSE, message=FALSE, warning=FALSE}
library(quantmod)


wk.JPM <- data.JPM
data.weekly.JPM <- to.weekly(wk.JPM)
data.weekly.JPM[c(1:3,nrow(data.weekly.JPM)),]

OHLC <- data.weekly.JPM[-1,-6]
JPM.ohlc <-
as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
JPM.ohlc[c(1:3,nrow(JPM.ohlc)),]

chartSeries(JPM.ohlc,theme="white.mono",name="JPM OHLC")


wk.GS <- data.GS
data.weekly.GS <- to.weekly(wk.GS)
data.weekly.GS[c(1:3,nrow(data.weekly.GS)),]

OHLC <- data.weekly.GS[-1,-6]
GS.ohlc <-
as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
GS.ohlc[c(1:3,nrow(GS.ohlc)),]

chartSeries(GS.ohlc,theme="white.mono",name="GS OHLC")

wk.AES <- data.AES
data.weekly.AES <- to.weekly(wk.AES)
data.weekly.AES[c(1:3,nrow(data.weekly.AES)),]

OHLC <- data.weekly.AES[-1,-6]
AES.ohlc <-
as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
AES.ohlc[c(1:3,nrow(AES.ohlc)),]

chartSeries(AES.ohlc,theme="white.mono",name="AES OHLC")

wk.DTE <- data.DTE
data.weekly.DTE <- to.weekly(wk.DTE)
data.weekly.DTE[c(1:3,nrow(data.weekly.DTE)),]

OHLC <- data.weekly.DTE[-1,-6]
DTE.ohlc <-
as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
DTE.ohlc[c(1:3,nrow(DTE.ohlc)),]

chartSeries(DTE.ohlc,theme="white.mono",name="DTE OHLC")

wk.AMZN <- data.AMZN
data.weekly.AMZN <- to.weekly(wk.AMZN)
data.weekly.AMZN[c(1:3,nrow(data.weekly.AMZN)),]

OHLC <- data.weekly.AMZN[-1,-6]
AMZN.ohlc <-
as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
AMZN.ohlc[c(1:3,nrow(AMZN.ohlc)),]

chartSeries(AMZN.ohlc,theme="white.mono",name="AMZN OHLC")


wk.AAPL <- data.AAPL
data.weekly.AAPL <- to.weekly(wk.AAPL)
data.weekly.AAPL[c(1:3,nrow(data.weekly.AAPL)),]

OHLC <- data.weekly.AAPL[-1,-6]
AAPL.ohlc <-
as.quantmod.OHLC(OHLC,col.names=c("Open","High","Low","Close","Volume"))
AAPL.ohlc[c(1:3,nrow(AAPL.ohlc)),]

chartSeries(AAPL.ohlc,theme="white.mono",name="AAPL OHLC")







```

Checking the gains during the pandemic from July 2019 to July 2021 for each sector
```{r sec4, echo=FALSE, message=FALSE, warning=FALSE}

JPM.Pandemic1 <- subset(data.JPM[,4], index(data.JPM) >= "2019-07-01" &index(data.JPM) < "2021-08-01")
GS.Pandemic1 <- subset(data.GS[,4], index(data.GS) >= "2019-07-01" &index(data.GS) < "2021-08-01")
AES.Pandemic1 <- subset(data.AES[,4], index(data.AES) >= "2019-07-01" &index(data.AES) < "2021-08-01")
DTE.Pandemic1 <- subset(data.DTE[,4], index(data.DTE) >= "2019-07-01" &index(data.DTE) < "2021-08-01")
AAPL.Pandemic1 <- subset(data.AAPL[,4], index(data.AAPL) >= "2019-07-01" &index(data.AAPL) < "2021-08-01")
AMZN.Pandemic1 <- subset(data.AMZN[,4], index(data.AMZN) >= "2019-07-01" &index(data.AMZN) < "2021-08-01")


#closing price data of all tickers

All.Close.Prices<-
cbind(JPM.Pandemic1$JPM.Close,GS.Pandemic1$GS.Close,AES.Pandemic1$AES.Close,DTE.Pandemic1$DTE.Close,AAPL.Pandemic1$AAPL.Close,AMZN.Pandemic1$AMZN.Close)
All.Close.Prices[c(1:3,nrow(All.Close.Prices)),]

#renaming the columns in dataframe
All.df<-cbind(index(All.Close.Prices),data.frame(All.Close.Prices))
ncol(All.df)
## [1] 7
names(All.df) <- paste(c("date","JPM","GS","AES","DTE", "AAPL", "AMZN"))
rownames(All.df) <- seq(1,nrow(All.df),1)
All.df[c(1:3,nrow(All.df)),]

All.df$Finance.idx <-(All.df$JPM+All.df$GS)/(All.df$GS[1]+All.df$JPM[1])
head(All.df$Finance.idx)

All.df$Utility.idx <-(All.df$AES+All.df$DTE)/(All.df$AES[1]+All.df$DTE[1])
head(All.df$Utility.idx)

All.df$Tech.idx <-(All.df$AAPL+All.df$AMZN)/(All.df$AAPL[1]+All.df$AMZN[1])
head(All.df$Tech.idx)
options(digits=5)


plot(x=All.df$date,y=All.df$Finance.idx,type="l",xlab="Date", ylab="Value of Investment ($)",ylim=c(0.2,2) ,col="blue",lty=1,lwd=1,
main="Value of $1 Investment in Financial, Utility and Tech sector 
between July 1st 2019 - July 31st 2021") 
lines(x=All.df$date, y=All.df$Utility.idx,col="red",lty=2,lwd=1)
lines(x=All.df$date,y=All.df$Tech.idx, col="green",lty=3,lwd=2)
abline(h=1,lty=1,col="black")
legend("topleft",c("Finance( JPM, GS)","Utility(DTE,AES)","Tech(AAPL,AMZN)"),col=c("blue","red","green"),lty=c(1,2,3),lwd=c(1
,1,1), box.lty = 0, cex =0.7)

```

Creating moving average for each sector

```{r movingAverage , echo=FALSE, message=FALSE, warning=FALSE}
library(TTR)
library(RcppParallel)
library(zoo)
JPM.sma<-data.JPM[,4]
GS.sma<-data.GS[,4]
Finance.sma<-JPM.sma+GS.sma
Finance.sma$sma50<-rollmeanr(Finance.sma$JPM.Close,k=50,fill=NA)
Finance.sma$sma200 <- rollmeanr(Finance.sma$JPM.Close,k=200, fill=NA)
Finance.smaPandemic<-subset(Finance.sma,index(Finance.sma)>="2019-07-01")
y.range <- range(Finance.sma,na.rm=TRUE)
Finance.smaPandemic[c(1:3,nrow(Finance.smaPandemic)),]

par(mfrow=c(1,1))
plot(x=index(Finance.smaPandemic),xlab = "Date",
y=Finance.smaPandemic$JPM.Close,ylim=y.range,col="red",lty=1,ylab="Price($)",type=
"l",
  main="Simple Moving Average for Finance sector July 2019 to July 2021")
lines(x=index(Finance.smaPandemic),y=Finance.smaPandemic$sma50,lty=2,col="Blue")
lines(x=index(Finance.smaPandemic),y=Finance.smaPandemic$sma200,lty=3, col ="Green")
legend("topleft",c("Finance","50-day moving average","200-day moving
average"),col=c("red","blue","Green"),lty=c(1,2,3))

AES.sma<-data.AES[,4]
DTE.sma<-data.DTE[,4]
Utility.sma<-AES.sma+DTE.sma
Utility.sma$sma50<-rollmeanr(Utility.sma$AES.Close,k=50,fill=NA)
Utility.sma$sma200 <- rollmeanr(Utility.sma$AES.Close,k=200, fill=NA)
Utility.smaPandemic<-subset(Utility.sma,index(Utility.sma)>="2019-07-01")
y.range <- range(Utility.sma,na.rm=TRUE)
Utility.smaPandemic[c(1:3,nrow(Utility.smaPandemic)),]

par(mfrow=c(1,1))
plot(x=index(Utility.smaPandemic),xlab = "Date",
y=Utility.smaPandemic$AES.Close,ylim=y.range,col="red",lty=1,ylab="Price($)",type=
"l",
  main="Simple Moving Average for Utility sector July 2019 to July 2021")
lines(x=index(Utility.smaPandemic),y=Utility.smaPandemic$sma50,lty=2,col="Blue")
lines(x=index(Utility.smaPandemic),y=Utility.smaPandemic$sma200,lty=3, col ="Green")
legend("bottomright",c("Utility","50-day moving average","200-day moving
average"),col=c("red","blue","Green"),lty=c(1,2,3))


AMZN.sma<-data.AMZN[,4]
AAPL.sma<-data.AAPL[,4]
Tech.sma<-AMZN.sma+AAPL.sma
Tech.sma$sma50<-rollmeanr(Tech.sma$AMZN.Close,k=50,fill=NA)
Tech.sma$sma200 <- rollmeanr(Tech.sma$AMZN.Close,k=200, fill=NA)
Tech.smaPandemic<-subset(Tech.sma,index(Tech.sma)>="2019-07-01")
y.range <- range(Tech.sma,na.rm=TRUE)
Tech.smaPandemic[c(1:3,nrow(Tech.smaPandemic)),]

par(mfrow=c(1,1))
plot(x=index(Tech.smaPandemic),xlab = "Date",
y=Tech.smaPandemic$AMZN.Close,ylim=y.range,col="red",lty=1,ylab="Price($)",type=
"l",
  main="Simple Moving Average for Tech sector July 2019 to July 2021")
lines(x=index(Tech.smaPandemic),y=Tech.smaPandemic$sma50,lty=2,col="Blue")
lines(x=index(Tech.smaPandemic),y=Tech.smaPandemic$sma200,lty=3, col ="Green")
legend("bottomright",c("Tech","50-day moving average","200-day moving
average"),col=c("red","blue","Green"),lty=c(1,2,3))
```

Bollinger BandsPlot for Pandemic Period
```{r sec 6 , echo=FALSE, message=FALSE, warning=FALSE}


JPM.bb<-JPM.Pandemic1
GS.bb<-GS.Pandemic1
DTE.bb<-DTE.Pandemic1
AES.bb<-AES.Pandemic1
AAPL.bb<-AAPL.Pandemic1
AMZN.bb<-AMZN.Pandemic1


Portfolio.bb<- cbind(JPM.bb$JPM.Close,GS.bb$GS.Close,DTE.bb$DTE.Close,AES.bb$AES.Close,AAPL.bb$AAPL.Close,AMZN.bb$AMZN.Close)
Portfolio.bb$all<- JPM.bb$JPM.Close+GS.bb$GS.Close+DTE.bb$DTE.Close+AES.bb$AES.Close+AAPL.bb$AAPL.Close+AMZN.bb$AMZN.Close
Portfolio.bb[c(1:3,nrow(Portfolio.bb)),]
Portfolio.bb$avg<-rollmeanr(Portfolio.bb$all,k=20)
Portfolio.bb$sd<-rollapply(Portfolio.bb$all,width=20, FUN=sd, fill=NA)
Portfolio.bb[c(1:3,nrow(Portfolio.bb)),]
Portfolio.bb$sd2up<-Portfolio.bb$avg+2*Portfolio.bb$sd
Portfolio.bb$sd2down<-Portfolio.bb$avg-2*Portfolio.bb$sd
Portfolio.bb[c(1:3,nrow(Portfolio.bb)),]


y.range <- range(Portfolio.bb[,-9],na.rm=TRUE)
plot(x=index(Portfolio.bb),xlab="Date",y=Portfolio.bb$all, col="pink",ylim =
y.range,ylab = "Price ($)",type = "l",lwd=2,     main=" Portfolio - Bollinger Bands (20 days, 2 deviations)
     July 1st 2019 - July  31,2021")
lines(x=index(Portfolio.bb),y=Portfolio.bb$avg,lty=2,col="gray",lwd=3)
lines(x=index(Portfolio.bb),y=Portfolio.bb$sd2up,col="blue")
lines(x=index(Portfolio.bb),y=Portfolio.bb$sd2down,col="orange")
legend("bottomright",c("Portfolio price","20-Day Moving Average","Upper
Band","Lower Band"),lty=c(1,2,1,1),lwd=c(2,3,1,1),
col=c("pink","gray","blue","orange"))
```
Portfolio return during the pandemic (Gross and Logarithmic)

```{r Portfolio price returns, echo=FALSE, message=FALSE, warning=FALSE}
library(xts)
multiPrice <- JPM.Pandemic1
multiPrice <- merge(multiPrice, GS.Pandemic1)
multiPrice <- merge(multiPrice, AES.Pandemic1)
multiPrice <- merge(multiPrice, DTE.Pandemic1)
multiPrice <- merge(multiPrice, AAPL.Pandemic1)
multiPrice <- merge(multiPrice, AMZN.Pandemic1)


library(quantmod)
multiPrice$JPM.Price.Ret = Delt(multiPrice$JPM.Close)
multiPrice$GS.Price.Ret = Delt(multiPrice$GS.Close)
multiPrice$DTE.Price.Ret = Delt(multiPrice$DTE.Close)
multiPrice$AES.Price.Ret = Delt(multiPrice$AES.Close)
multiPrice$AAPL.Price.Ret = Delt(multiPrice$AAPL.Close)
multiPrice$AMZN.Price.Ret = Delt(multiPrice$AMZN.Close)
multiPrice[c(1:4, nrow(multiPrice)), ]

multiPrice$Port.Ret = Delt(
  multiPrice$JPM.Close + multiPrice$GS.Close + multiPrice$DTE.Close + multiPrice$AES.Close+ multiPrice$AAPL.Close + multiPrice$AMZN.Close
)
PortfioReturn <- prod(multiPrice$Port.Ret[2:nrow(multiPrice), ] + 1) - 1
PortfioReturn
```
```{r grossReturns, echo=FALSE, message=FALSE, warning=FALSE}

multiple <- data.JPM.Pandemic[,4:5]
multiple <-merge(multiple,data.GS.Pandemic[,4:5])
multiple <-merge(multiple,data.AES.Pandemic[,4:5])
multiple <-merge(multiple,data.DTE.Pandemic[,4:5])
multiple <-merge(multiple,data.AMZN.Pandemic[,4:5])
multiple <-merge(multiple,data.AAPL.Pandemic[,4:5])

head(multiple)
multiple$JPM.Ret=Delt(multiple$JPM.Adjusted)
multiple$AES.Ret=Delt(multiple$AES.Adjusted)
multiple$DTE.Ret=Delt(multiple$DTE.Adjusted)
multiple$GS.Ret=Delt(multiple$GS.Adjusted)
multiple$AAPL.Ret=Delt(multiple$AAPL.Adjusted)
multiple$AMZN.Ret=Delt(multiple$AMZN.Adjusted)

head(data.AES.Pandemic$AES.Adjusted)
multiple$Port.Tot.Ret<- Delt(multiple$JPM.Adjusted+multiple$GS.Adjusted+multiple$AES.Adjusted+multiple$DTE.Adjusted+multiple$AMZN.Adjusted+multiple$AAPL.Adjusted)


multiple$Port.Log.Tot.Ret<-log(multiple$Port.Tot.Ret+1)
multiple[1:5,]

LogReturenDifference<-multiple$Port.Tot.Ret-multiple$Port.Log.Tot.Ret
plot(LogReturenDifference)

```

Plot a comparison of Total Price returns and Total Gross returns
```{r plot price return vs gross return, echo=FALSE, message=FALSE, warning=FALSE}

multiPrice<-multiPrice[-1,]
multiPrice$indexV<-cumprod(multiPrice$Port.Ret+1)
multiple<-multiple[-1,]
multiple$TotalV<-cumprod(multiple$Port.Tot.Ret+1)

plot(multiPrice$index,type ="l",xlab ="Date",ylab ="Return",col="blue",main ="Price Returns vs. Total Gross Returns")
lines(multiple$TotalV,col='gray')
```


Creating a equally weighted portfolio 
```{r equally weighted portfolio, echo=FALSE, message=FALSE, warning=FALSE}
multiple1 <-data.JPM.Pandemic[,5]
multiple1 <-merge(multiple1,data.GS.Pandemic[,5])
multiple1 <-merge(multiple1,data.AES.Pandemic[,5])
multiple1 <-merge(multiple1,data.DTE.Pandemic[,5])
multiple1 <-merge(multiple1,data.AMZN.Pandemic[,5])
multiple1 <-merge(multiple1,data.AAPL.Pandemic[,5])

multiple1$JPM.Ret=Delt(multiple1$JPM.Adjusted)
multiple1$GS.Ret=Delt(multiple1$GS.Adjusted)
multiple1$AES.Ret=Delt(multiple1$AES.Adjusted)
multiple1$DTE.Ret=Delt(multiple1$DTE.Adjusted)
multiple1$AAPL.Ret=Delt(multiple1$AAPL.Adjusted)
multiple1$AMZN.Ret=Delt(multiple1$AMZN.Adjusted)

#First Half EW Port Value
ew.h1 <-subset(multiple1, index(multiple1)>"2019-07-01")
ew.h1 <-subset(ew.h1, index(ew.h1)<"2020-01-01")
ew.h1[c(1:4,nrow(ew.h1)),]

ew.h1$JPM <-cumprod(ew.h1$JPM.Ret+1)
ew.h1$GS <-cumprod(ew.h1$GS.Ret+1)
ew.h1$DTE <-cumprod(ew.h1$DTE.Ret+1)
ew.h1$AES <-cumprod(ew.h1$AES.Ret+1)
ew.h1$AAPL <-cumprod(ew.h1$AAPL.Ret+1)
ew.h1$AMZN <-cumprod(ew.h1$AMZN.Ret+1)
ew.h1$EWPort<-(ew.h1$GS+ew.h1$JPM+ew.h1$AAPL+ew.h1$AMZN+ew.h1$DTE+ew.h1$AES)/6
ew.h1$EWRet<-rbind(ew.h1$EWPort[1]-1,Delt(ew.h1$EWPort)[-1,])

#H2: EW Port value

ew.h2 <-subset(multiple1, index(multiple1)>="2020-01-011")
ew.h2 <-subset(ew.h2, index(ew.h2)<"2020-07-01")
ew.h2[c(1:4,nrow(ew.h2)),]

ew.h2$JPM <-cumprod(ew.h2$JPM.Ret+1)
ew.h2$GS <-cumprod(ew.h2$GS.Ret+1)
ew.h2$DTE <-cumprod(ew.h2$DTE.Ret+1)
ew.h2$AES <-cumprod(ew.h2$AES.Ret+1)
ew.h2$AAPL <-cumprod(ew.h2$AAPL.Ret+1)
ew.h2$AMZN <-cumprod(ew.h2$AMZN.Ret+1)
ew.h2$EWPort<-(ew.h2$GS+ew.h2$JPM+ew.h2$AAPL+ew.h2$AMZN+ew.h2$DTE+ew.h2$AES)/6

ew.h2$EWRet<-rbind(ew.h2$EWPort[1]-1,Delt(ew.h2$EWPort)[-1,])

#H3: EW Port value

ew.h3 <-subset(multiple1, index(multiple1)>="2020-07-01")
ew.h3 <-subset(ew.h3, index(ew.h3)<"2021-01-01")
ew.h3[c(1:4,nrow(ew.h3)),]

ew.h3$JPM <-cumprod(ew.h3$JPM.Ret+1)
ew.h3$GS <-cumprod(ew.h3$GS.Ret+1)
ew.h3$DTE <-cumprod(ew.h3$DTE.Ret+1)
ew.h3$AES <-cumprod(ew.h3$AES.Ret+1)
ew.h3$AAPL <-cumprod(ew.h3$AAPL.Ret+1)
ew.h3$AMZN <-cumprod(ew.h3$AMZN.Ret+1)
ew.h3$EWPort<-(ew.h3$GS+ew.h3$JPM+ew.h3$AAPL+ew.h3$AMZN+ew.h3$DTE+ew.h3$AES)/6

ew.h3$EWRet<-rbind(ew.h3$EWPort[1]-1,Delt(ew.h3$EWPort)[-1,])

#H4
ew.h4 <-subset(multiple1, index(multiple1)>="2021-01-01")
ew.h4 <-subset(ew.h4, index(ew.h4)<"2021-07-01")
ew.h4[c(1:4,nrow(ew.h4)),]

ew.h4$JPM <-cumprod(ew.h4$JPM.Ret+1)
ew.h4$GS <-cumprod(ew.h4$GS.Ret+1)
ew.h4$DTE <-cumprod(ew.h4$DTE.Ret+1)
ew.h4$AES <-cumprod(ew.h4$AES.Ret+1)
ew.h4$AAPL <-cumprod(ew.h4$AAPL.Ret+1)
ew.h4$AMZN <-cumprod(ew.h4$AMZN.Ret+1)
ew.h4$EWPort<-(ew.h4$GS+ew.h4$JPM+ew.h4$AAPL+ew.h4$AMZN+ew.h4$DTE+ew.h4$AES)/6

ew.h4$EWRet<-rbind(ew.h4$EWPort[1]-1,Delt(ew.h4$EWPort)[-1,])

ew.all<-rbind(ew.h1,ew.h2,ew.h3,ew.h4)
ew.all$portvalue<-cumprod(ew.all$EWRet+1)
head(ew.all)

y.range<-range(ew.all[,2:3])
plot(ew.all$portvalue,col="blue",main="Equally-weighted Half yearly performance
     ")
```

```{r quarterly, echo=FALSE, message=FALSE, warning=FALSE}
portfolio <-cbind(data.frame(index(multiple)), data.frame(multiple))
names(portfolio)[1] <-paste("date")
#portfolio[c(1:3, nrow(portfolio)), ]
vwport<-portfolio
#vwport[c(1:3,nrow(portfolio)),]
#changing index of vwportfolio to observation number
rownames(vwport) <- seq(1:nrow(vwport))
#vwport[c(1:3,nrow(vwport)), ]

#converting net returns to gross returns
vwport$JPM.Ret <- 1+ vwport$JPM.Ret
vwport$GS.Ret <- 1+ vwport$GS.Ret
vwport$DTE.Ret <- 1+ vwport$DTE.Ret
vwport$AES.Ret <- 1+ vwport$AES.Ret
vwport$AMZN.Ret <- 1+vwport$AMZN.Ret
vwport$AAPL.Ret <- 1+vwport$AAPL.Ret
vwport[c(1:3,nrow(vwport)),]


#Constructing series of calendar days
date <-seq(as.Date("2019-07-01"), as.Date("2021-07-01"), by =1)
date <-data.frame(date)
date[c(1:3, nrow(date)), ]
#Creating a data object with daily with last available price on non-trading days
PRICE.qtr<-vwport
PRICE.qtr[c(1:3, nrow(PRICE.qtr)), ]

## Keep only prices at the end of each calendar half
PRICE.qtr <-subset(PRICE.qtr, PRICE.qtr$date == as.Date("2019-12-31")| PRICE.qtr$date ==as.Date("2020-06-30") | PRICE.qtr$date ==as.Date("2020-12-31")| PRICE.qtr$date ==as.Date("2021-06-30"))
head(PRICE.qtr)


#total outstanding shares at the end of each half

PRICE.qtr$JPM.shout <-c(2.988e+09,3.049e+09,3.048e+09,3.084e+09)
PRICE.qtr$GS.shout <-c(337.28e+06,344.09e+06,343.94e+06,347.34e+06) 
PRICE.qtr$DTE.shout <-c(193.75e+06,193.77e+06,192.65e+06,192.21e+06)
PRICE.qtr$AES.shout <-c(666.33e+06,665.37e+06,664.94e+06,664.04e+06) 
PRICE.qtr$AMZN.shout <-c(506.00e+06,503.00e+06,501.00e+06,498.00e+06)
PRICE.qtr$AAPL.shout <-c(16.56e+09,16.82e+09,17.14e+09,17.54e+09)
str(PRICE.qtr)

weights <-PRICE.qtr
weights$JPM.mcap <-weights$JPM.Close*weights$JPM.shout
weights$DTE.mcap <-weights$DTE.Close*weights$DTE.shout
weights$AES.mcap <-weights$AES.Close*weights$AES.shout
weights$AMZN.mcap <-weights$AMZN.Close*weights$AMZN.shout
weights$GS.mcap <-weights$GS.Close *weights$GS.shout
weights$AAPL.mcap <-weights$AAPL.Close *weights$AAPL.shout
weights$tot.mcap <-rowSums(weights[10:13]) #change col number weights

weights$JPM.wgt <-weights$JPM.mcap/weights$tot.mcap
weights$GS.wgt <-weights$GS.mcap/weights$tot.mcap
weights$AMZN.wgt <-weights$AMZN.mcap/weights$tot.mcap
weights$AAPL.wgt <-weights$AAPL.mcap/weights$tot.mcap
weights

WEIGHT <-weights[, c(1, 15:18)]
#change col number WEIGHT
vwret <-na.locf(merge(date, WEIGHT, by ="date", all.x =TRUE))
vwret[c(1:3, nrow(vwret)), ]

str(vwret)
```


a)Construct a variance-covariance matrix
```{r com, , echo=FALSE, message=FALSE, warning=FALSE}
#Combining the two series

AAPL.ret <-Delt(data.AAPL.Pandemic$AAPL.Adjusted)
AAPL.ret[c(1:3,nrow(AAPL.ret)),]

AMZN.ret <-Delt(data.AMZN.Pandemic$AMZN.Adjusted)
AMZN.ret[c(1:3,nrow(AMZN.ret)),]

DTE.ret <-Delt(data.DTE.Pandemic$DTE.Adjusted)
DTE.ret[c(1:3,nrow(DTE.ret)),]

AES.ret <-Delt(data.AES.Pandemic$AES.Adjusted)
AES.ret[c(1:3,nrow(AES.ret)),]

JPM.ret <-Delt(data.JPM.Pandemic$JPM.Adjusted)
JPM.ret[c(1:3,nrow(JPM.ret)),]

GS.ret <-Delt(data.GS.Pandemic$GS.Adjusted)
GS.ret[c(1:3,nrow(GS.ret)),]



returns <-cbind(AAPL.ret, AMZN.ret, JPM.ret, GS.ret, AES.ret, DTE.ret)
names(returns) <-paste(c("AAPL.Ret","AMZN.Ret","JPM.Ret","GS.Ret","AES.Ret","DTE.Ret"))
returns <-returns[-1,]
returns[c(1:3,nrow(return)),]

#Creating vector weights with 20% AAPL, 15% AMZN, 5% JPM, 15% GS, AES 25%, DTE 20%

WGT.2asset <-c(0.20,.15,.05,.15,.25,.20)
WGT.2asset <-matrix(WGT.2asset,1)
WGT.2asset
#Creating transposed vector of weights

tWGT.2asset <-t(WGT.2asset)
tWGT.2asset

#Constructing Variance-Covariance Matrix and converting returns into a matrix using as.matrix command
mat.Ret <-as.matrix(returns)
head(mat.Ret)

#Calculating the covariance using cov command
options(scipen ="100")
cov(mat.Ret)

#Annualizing the variances and covariances: multiplying the matrix by 249

VCOV.2asset <-cov(mat.Ret)*504
VCOV.2asset

#install.packages('zoo')
library(xts)
library(zoo)
```

Equally Weighted portfolio

```{r AAPLE, echo=FALSE, message=FALSE, warning=FALSE}
library(slam)
library(cccp)
library(FRAPO)
library(ghyp)
library(timeSeries)
library(fBasics)
library(timeDate)

#Ew Portfolio
EWPort<-(GS.Pandemic$Open+JPM.Pandemic$Open+AAPL.Pandemic$Open+AMZN.Pandemic$Open+DTE.Pandemic$Open+AES.Pandemic$Open)/6


date<- index(GS.Pandemic) 
OpeningPrice<-EWPort
attr(OpeningPrice, 'time')<-date
#Creating a variable that represent daily returns by using returnseries() (part of FRAPO package) function.
#Variable is named as EWPortRet
#The function “returnseries” from the FRAPO package is used to compute financial returns from prices or indexes.
EWPortRet<-returnseries(OpeningPrice)
EWPortLoss <- -1* EWPortRet
hist(EWPortLoss, breaks = 100)
hist(EWPortRet, breaks = 100)

attr(EWPortRet, 'time')<-date

datets<-as.character(date)
EWPortTimeS<-timeSeries(EWPortRet, charvec = datets)
str(EWPortTimeS)

##plot the density function for the timeseries EWPortTimeS
EWPort.ef<-density(EWPortTimeS, na.rm=TRUE)
plot(EWPort.ef)

#Fit the Generalized Hyperbolic Distribution
ghdfit<- fit.ghypuv(EWPortTimeS, symmetric =FALSE, control =list(maxit =1000), na.rm =TRUE)

hypfit<-fit.hypuv(EWPortTimeS, symmetric =FALSE, control =list(maxit =1000),na.rm =TRUE)

#Fit the Normal Inverse Gaussian Distribution
nigfit<-fit.NIGuv(EWPortTimeS, symmetric =FALSE, control =list(maxit =1000), na.rm =TRUE)

```










Obtaining the density functions and plot for AAPL
```{r sd EWPort, echo=FALSE, message=FALSE, warning=FALSE}
ghddens.EWPort <-dghyp(EWPort.ef$x, ghdfit)
hypdens.EWPort <-dghyp(EWPort.ef$x, hypfit)
nigdens.EWPort <-dghyp(EWPort.ef$x, nigfit)
nordens.EWPort <-dnorm(EWPort.ef$x, mean =mean(EWPortTimeS, na.rm=TRUE), sd =sd(c(EWPortTimeS[,1]), na.rm=TRUE))
col.def <-c("black", "red", "blue", "green", "orange")
plot(EWPort.ef, xlab ="", ylab =expression(f(x)), ylim =c(0, 0.35))
lines(EWPort.ef$x, ghddens.EWPort, col ="red")
lines(EWPort.ef$x, hypdens.EWPort, col ="blue")
lines(EWPort.ef$x, nigdens.EWPort, col ="green")
lines(EWPort.ef$x, nordens.EWPort, col ="orange")
legend("topright",legend =c("empirical", "GHD", "HYP", "NIG", "NORM"),col =col.def, lty =1)
```
QQ Plot for EWPort
```{r qq EWPort,echo=FALSE, message=FALSE, warning=FALSE}
qqghyp(ghdfit, line =TRUE, ghyp.col ="red", plot.legend =FALSE,gaussian=FALSE, main ="", cex =0.8)
qqghyp(hypfit, add =TRUE, ghyp.pch =2, ghyp.col ="blue",gaussian =FALSE, line=FALSE, cex =0.8)
qqghyp(nigfit, add =TRUE, ghyp.pch =3, ghyp.col ="green",gaussian =FALSE, line =FALSE, cex =0.8)
legend("topleft", legend =c("GHD", "HYP", "NIG"),col = col.def[-c(1,5)], pch =1:3)
```
Best fit Model
#Use the function “lik.ratio.test” to perform a likelihood-ratio test on fitted generalized hyperbolic distribution objects of class mle.ghyp. The likelihood-ratio test can be used to check whether a special case of the generalized hyperbolic distribution is the “true” underlying distribution.
#statistic: the value of the L-statistic.
#p.value: the p-value for the test (the p-value is less than 0.05, then there is evidence against the null hypothesis)
#df: the degrees of freedom for the L-statistic
#H0: a boolean stating whether the null hypothesis is TRUE or FALSE (if TRUE there is no relationship between the data sets)
```{r modelaaaa ,echo=FALSE, message=FALSE, warning=FALSE}
AIC <-stepAIC.ghyp(EWPortTimeS, control =list(maxit =1000))
head(AIC$fit.table)

LRghdnig <-lik.ratio.test(ghdfit, nigfit)
LRghdnig

LRghdhyp <-lik.ratio.test(ghdfit, hypfit)
```

The VaR based on the normal distribution can be computed by providing the necessary estimates for the location and scale.
The VaR values thus determined are compared to their empirical counterparts, which are determined by the quantile() function.

```{r someeee,echo=FALSE, message=FALSE, warning=FALSE}
p <-seq(0.001, 0.05, 0.001)
ghd.VaR <-abs(qghyp(p, ghdfit))
hyp.VaR <-abs(qghyp(p, hypfit))
nig.VaR <-abs(qghyp(p, nigfit))
nor.VaR <-abs(qnorm(p, mean =mean(EWPortTimeS, na.rm=TRUE), sd =sd(c(EWPortTimeS[,1]), na.rm =TRUE)))
emp.VaR <-abs(quantile(x = EWPortTimeS, probs = p, na.rm=TRUE))

plot(emp.VaR, type ="l", xlab ="", ylab ="VaR", axes =FALSE, ylim =range(c(hyp.VaR, nig.VaR, ghd.VaR, nor.VaR, emp.VaR)))
box()
axis(1, at =seq(along = p), labels =names(emp.VaR), tick =FALSE)
axis(2, at =pretty(range(emp.VaR, ghd.VaR, hyp.VaR, nig.VaR,
                         nor.VaR)))
lines(seq(along = p), ghd.VaR, col ="red")
lines(seq(along = p), hyp.VaR, col ="blue")
lines(seq(along = p), nig.VaR, col ="green")
lines(seq(along = p), nor.VaR, col ="orange")
legend("topright",
       legend =c("Empirical", "GHD", "HYP", "NIG", "Normal"),
       col = col.def, lty =1)
```


Calculate and plot the Expected Shortfall (using all models)
```{r es,echo=FALSE, message=FALSE, warning=FALSE}
ghd.ES <-abs(ESghyp(p, ghdfit))
hyp.ES <-abs(ESghyp(p, hypfit))
nig.ES <-abs(ESghyp(p, nigfit))
nor.ES <-abs(mean(EWPortTimeS, na.rm=TRUE) -sd(c(EWPortTimeS[, 1]),na.rm =TRUE)
             *dnorm(qnorm(1-p)) /p)
obs.p <-ceiling(p *length(EWPortTimeS))
emp.ES <-sapply(obs.p, function(x) abs(mean(sort(c(EWPortTimeS))[1:x])))
# Plot the ES
plot(emp.ES, type ="l", xlab ="", ylab ="ES", axes =FALSE,ylim =range(c(hyp.ES, nig.ES, ghd.ES, nor.ES, emp.ES),na.rm =TRUE))
box()
axis(1, at =1:length(p), labels =names(emp.VaR), tick =FALSE)
axis(2, at =pretty(range(emp.ES, ghd.ES, hyp.ES, nig.ES, nor.ES)))
lines(1:length(p), ghd.ES, col ="red")
lines(1:length(p), hyp.ES, col ="blue")
lines(1:length(p), nig.ES, col ="green")
lines(1:length(p), nor.ES, col ="orange")
legend("topright",legend =c("Empirical", "GHD", "HYP", "NIG", "Normal"),col =
col.def, lty =1)
```

Garch Model 
```{r Model Fitting for equally Weighted portfolio, echo = TRUE}

EWPort.AdjClose<-(GS.Pandemic$Adj.Close+JPM.Pandemic$Adj.Close+AAPL.Pandemic$Adj.Close+AMZN.Pandemic$Adj.Close+DTE.Pandemic$Adj.Close+AES.Pandemic$Adj.Close)/6

EWPortReturn<-returnseries(EWPort.AdjClose)
library(timeSeries)
library('fGarch')

date<-JPM$Date
str(date)


GETS<-timeSeries(EWPortReturn, charvec = date)
GETS$Return <- GETS[-c(1)]
head(GETS$Return)
acf(GETS$Return, na.action = na.pass)
pacf(GETS$Return, na.action = na.pass)

acf(abs(GETS$Return), na.action = na.pass)
pacf(abs(GETS$Return), na.action = na.pass)

mean(GETS$Return, na.rm = TRUE)
GETSComp <- removeNA(GETS)

garchFi<-garchFit(~garch(1,1), data=GETSComp)


a <- coef(garchFi)
b<-formula(garchFi)
c<-volatility(garchFi)
plot(c)

predict(garchFi, n.ahead =10)
# with SD
garchfi2<-garchFit(~garch(1,1), data=GETSComp, cond.dist = "std")
sigma <-  as.numeric(predict(garchfi2, n.ahead = 1)[3])
df <- as.numeric(coef(garchfi2)["shape"])
rand<-rt(100000, df=df)
hist(rand, breaks=100)
quant<-qt(.01, df=df)
a<-sigma*quant #VaR
b<-max(tail(sort(rand, decreasing = T),1000))*sigma #VaR
a/b

d<-mean(tail(sort(rand, decreasing = T),1000))*sigma #ES
head(d/c)




```
Markvitz Optimization 

```{r optimization, message=FALSE, warning=FALSE, error=FALSE}
library(xts)
library(quantmod)
library(readxl)


JPM.Monthly<-to.monthly(data.JPM.Pandemic)
GS.Monthly<-to.monthly(data.GS.Pandemic)
DTE.Monthly<-to.monthly(data.DTE.Pandemic)
AES.Monthly<-to.monthly(data.AES.Pandemic)
AAPL.Monthly<-to.monthly(data.AAPL.Pandemic)
AMZN.Monthly<-to.monthly(data.AMZN.Pandemic)

AMZN.monthly.ret <-Delt(AMZN.Monthly$data.AMZN.Pandemic.Adjusted)
names(AMZN.monthly.ret)<-paste("AMZN.ret.monthly")
AMZN.monthly.ret[c(1:3,nrow(AMZN.monthly.ret))]

JPM.monthly.ret <-Delt(JPM.Monthly$data.JPM.Pandemic.Adjusted)
names(JPM.monthly.ret)<-paste("JPM.ret.monthly")
JPM.monthly.ret[c(1:3,nrow(JPM.monthly.ret))]

GS.monthly.ret <-Delt(GS.Monthly$data.GS.Pandemic.Adjusted)
names(GS.monthly.ret)<-paste("GS.ret.monthly")
GS.monthly.ret[c(1:3,nrow(GS.monthly.ret))]

DTE.monthly.ret <-Delt(DTE.Monthly$data.DTE.Pandemic.Adjusted)
names(DTE.monthly.ret)<-paste("DTE.ret.monthly")
DTE.monthly.ret[c(1:3,nrow(DTE.monthly.ret))]

AES.monthly.ret <-Delt(AES.Monthly$data.AES.Pandemic.Adjusted)
names(AES.monthly.ret)<-paste("AES.ret.monthly")
AES.monthly.ret[c(1:3,nrow(AES.monthly.ret))]

AAPL.monthly.ret <-Delt(AAPL.Monthly$data.AAPL.Pandemic.Adjusted)
names(AAPL.monthly.ret)<-paste("AAPL.ret.monthly")
AAPL.monthly.ret[c(1:3,nrow(AAPL.monthly.ret))]


```



```{r combining monthly return series,message=FALSE, warning=FALSE, error=FALSE}
options(digits=3)
returns <-
cbind(JPM.monthly.ret[-1,],GS.monthly.ret[-1,],AES.monthly.ret[-1,],DTE.monthly.ret[-1,],AAPL.monthly.ret[-1,],AMZN.monthly.ret[-1,])
names(returns) <-
paste(c("JPM.Ret","GS.Ret","AES.Ret","DTE.Ret","AAPL.Ret","AMZN.Ret"))
returns[c(1:3,nrow(returns)),]
#Converting data to matrix
mat.ret<-matrix(returns,nrow(returns))
mat.ret [1:3,]

colnames(mat.ret) <- c("JPM","GS","AES","DTE","AAPL","AMZN")
head(mat.ret)
VCOV <- cov(mat.ret)
VCOV

```

```{r 1b,message=FALSE, warning=FALSE, error=FALSE}
library(quadprog)
avg.ret <- matrix(apply(mat.ret,2,mean))
colnames(avg.ret) <- paste("Avg.Ret")
rownames(avg.ret) <-
paste(c("JPM","GS","AES","DTE","AAPL","AMZN"))
avg.ret

#set the smaller of the average returns as minimum return min.ret and the larger of the average returns as the max return max.ret.
min.ret <- min(avg.ret)
min.ret

max.ret <- max(avg.ret)
max.ret

# Create a sequence that begins with min.ret and ends with max.ret with 100 increments in between.

increments = 100
tgt.ret <- seq(min.ret,max.ret,length=increments)
head(tgt.ret)
tail(tgt.ret)

#Construct Dummy Portfolio Standard Deviation Vector
tgt.sd <- rep(0,length=increments)
tgt.sd
wgt <- matrix(0,nrow=increments,ncol=length(avg.ret))

head(wgt)

tail(wgt)

#Run the quadprog Optimizer

for (i in 1:increments) {
Dmat <- 2*VCOV
dvec <- c(rep(0,length(avg.ret)))
Amat <- cbind(rep(1,length(avg.ret)),avg.ret,diag(1,nrow=ncol(returns))) 
bvec <- c(1,tgt.ret[i],rep(0,ncol(returns)))
soln <- solve.QP(Dmat,dvec,Amat,bvec=bvec)
tgt.sd[i] <- sqrt(soln$value)
wgt[i,] <- soln$solution}

head(tgt.sd)
tail(tgt.sd)
options(scipen=100)
head(wgt)

# Overwrite the first entries, thaty are not zero due to a calculation error.Also rename the column headers.
colnames(wgt) <-
paste(c("wgt.JPM","wgt.GS","wgt.AES","wgt.DTE","wgt.AAPL","wgt.AMZN"))



wgt[1,1] <- 0
wgt[nrow(wgt),2] <- 0
head(wgt)

# Combine Portfolio Returns, Portfolio Standard Deviations, and PortfolioWeights
tgt.port <- data.frame(cbind(tgt.ret,tgt.sd,wgt))
head(tgt.port)

minvar.port <-subset(tgt.port,tgt.port$tgt.sd==min(tgt.port$tgt.sd))
head(minvar.port)
```


```{r tangency portfolio, message=FALSE, warning=FALSE, error=FALSE}
#3-month treasury as of end of Dec-31-2020 was 0.09%
riskfree = .0009/12
tgt.port$Sharpe <- (tgt.port$tgt.ret-riskfree)/tgt.port$tgt.sd
head(tgt.port)


# Identify the portfolio with the highest Sharpe Ratio and that is the tangency portfolio.

tangency.port <-subset(tgt.port,tgt.port$Sharpe==max(tgt.port$Sharpe))
tangency.port
```

Plot the Mean-Variance (MV) Efficient Frontier
```{r 1d , message=FALSE, warning=FALSE, error=FALSE}
eff.frontier <-subset(tgt.port,tgt.port$tgt.ret>=minvar.port$tgt.ret)
eff.frontier[c(1:3,nrow(eff.frontier)),]

plot(x=tgt.sd,
     y=tgt.ret,
     col="green",
     xlab="Portfolio Risk",
     ylab="Portfolio Return",
    main="Mean-Variance(MV) Efficient Frontier of Portfolio- Six
     Securities Based on the Quadratic Programming Approach")
abline(h=0,lty=1)
points(x=minvar.port$tgt.sd,y=minvar.port$tgt.ret,pch=17,cex=3)
points(x=tangency.port$tgt.sd,y=tangency.port$tgt.ret,pch=19,cex=3)
points(x=eff.frontier$tgt.sd,y=eff.frontier$tgt.ret)
```
Diversification Benefits
```{r B, message=FALSE, warning=FALSE, error=FALSE}
library(FRAPO)
library(lattice)

Idx <- interpNA(returns, method = "before")
R <- returnseries(Idx, method = "discrete", trim = TRUE)
V <- cov(R)
head(Idx)
# The allocations according to the four portfolio optimizations are then extracted by means of the Weights() method and assigned to the objects GMVw, MDPw, MTDw, and ERCw for the global-minimum variance, most-diversified, minimum tail-dependent, and equal-risk contributed solutions, respectively.
```

  1.The global-minimum variance portfolio.
```{r B1, message=FALSE, warning=FALSE, error=FALSE}
GMVw <- Weights(PGMV(R))
```
  2.The most diversified Portfolio,
```{r B2, message=FALSE, warning=FALSE, error=FALSE}
MDPw <- Weights(PMD(R))

```
  3.The equal-risk contributed Portfolio
```{r B3, message=FALSE, warning=FALSE, error=FALSE}
ERCw <- Weights(PERC(V))
```
  4.Minimum tail-dependent portfolio
```{r B4, message=FALSE, warning=FALSE, error=FALSE}
MTDw <- Weights(PMTD(R))

```
  
```{r graphs , message=FALSE, warning=FALSE, error=FALSE}
# The weights are then collected in the matrix object W. This object is then used in the call to the apply() function to determine the marginal risk contributions for each of the four optimal weight vectors.

W <- cbind(GMVw, MDPw, MTDw, ERCw)
MRC <- apply(W, 2, mrc, Sigma = V)
rownames(MRC) <- colnames(Idx)

colnames(MRC) <- c("GMV", "MDP", "MTD", "ERC")
oldpar <- par(no.readonly = TRUE)

par(mfrow = c(2, 2))
dotchart(GMVw, xlim = c(0, 40), main = "GMV Allocation", pch = 19)
dotchart(MDPw - GMVw, xlim = c(-20, 20), main = "MDP vs. GMV",
         pch = 19)
abline(v = 0, col = "blue")
dotchart(MTDw - GMVw, xlim = c(-20, 20), main = "MTD vs. GMV", pch = 19)
abline(v = 0, col = "blue")
dotchart(ERCw - GMVw, xlim = c(-20, 20), main = "ERC vs. GMV",
pch = 19)
abline(v = 0, col = "blue")

library(PerformanceAnalytics)
Rdec <- R / 100
Pret <- apply(W, 2, function(x) Rdec %*% x / 100)
SD <- apply(Pret, 2, sd) * 100
ES95 <- apply(Pret, 2, function(x)
  abs(ES(R = x, method = "modified") * 100))
## Summarising results
Res <- rbind(SD, ES95)
Res
```
  
  
